\chapter*{Foreword and acknowledgments}


This is a draft text intended for a class on operating systems. It
explains the main concepts of operating systems by studying an example
kernel, named xv6.  Xv6 is modeled on Dennis Ritchie's and
Ken Thompson's Unix Version 6 (v6)~\cite{unix}.  Xv6 loosely follows the structure
and style of v6, but is implemented in ANSI C~\cite{kernighan} for 
a multi-core RISC-V~\cite{riscv}.

這是為作業系統課程準備的文字草稿。 它
透過研究範例解釋作業系統的主要概念
內核，命名為xv6。 Xv6 以丹尼斯·里奇 (Dennis Ritchie) 為藍本
Ken Thompson 的 Unix 版本 6 (v6)~\cite{unix}。 Xv6 鬆散地遵循該結構
和 v6 的風格，但在 ANSI C~\cite{kernighan} 中實現
多核心 RISC-V~\cite{riscv}。\\

This text should be read along with the source code for xv6, an approach 
inspired by John Lions' Commentary on UNIX 6th Edition~\cite{lions}. See
\url{https://pdos.csail.mit.edu/6.1810} for pointers to on-line
resources for v6 and xv6, including several lab assignments
using xv6.

本文應與 xv6 的源代碼一起閱讀，xv6 是一種方法
靈感來自 John Lions 的 UNIX 第六版評論~\cite{lions}。 看
\url{https://pdos.csail.mit.edu/6.1810} 取得線上鏈接
v6 和 xv6 的資源，包括多個實驗室作業
使用xv6。\\

We have used this text in 6.828 and 6.1810, the operating system
classes at MIT.  We thank the faculty, teaching assistants, and
students of those classes who have all directly or indirectly
contributed to xv6.  In particular, we would like to thank Adam Belay,
Austin Clements, and Nickolai Zeldovich.  Finally, we would like to
thank people who emailed us bugs in the text or suggestions for
improvements: Abutalib Aghayev, Sebastian Boehm, brandb97, Anton
Burtsev, Raphael Carvalho, Tej Chajed, Rasit Eskicioglu, Color Fuzzy,
Wojciech Gac, Giuseppe, Tao Guo, Haibo Hao, Naoki Hayama, Chris
Henderson, Robert Hilderman, Eden Hochbaum, Wolfgang Keller, Henry
Laih, Jin Li, Austin Liew, Pavan Maddamsetti, Jacek Masiulaniec,
Michael McConville, m3hm00d, miguelgvieira, Mark Morrissey, Muhammed
Mourad, Harry Pan, Harry Porter, Siyuan Qian, Askar Safin, Salman
Shah, Huang Sha, Vikram Shenoy,  Adeodato Simó, Ruslan Savchenko, Pawel Szczurko,
Warren Toomey, tyfkda, tzerbib, Vanush Vaswani, Xi Wang, and Zou Chang
Wei, Sam Whitlock, LucyShawYang, and Meng Zhou\\

If you spot errors or have suggestions for improvement, please send email to
Frans Kaashoek and Robert Morris (kaashoek,rtm@csail.mit.edu).

如果您發現錯誤或有改進建議，請發送電子郵件至
Frans Kaashoek和Robert Morris(kaashoek,rtm@csail.mit.edu).